The \kepler Smear Campaign I: An Asteroseismic Catalogue of Bright Red Giants

### 2018-09-14 paper/ms.tex
simon and conny agree that it is chemically peculiar spot variation

Two other stars whose variability we classify as rotational modulation, HD~176582 (B5V) and HD~179395 (B9), have very short periods (1.58~d and 1.83~d respectively) and phase stability throughout the \kepler observations. While HD~176582 is listed as an eruptive variable by \citet{2016ApJ...829...23D}, this appears to be a misclassification considering the full \kepler smear light curve. Both stars show periods shorter than the shortest `heartbeat' binaries with tidally-induced pulsations from \citet{2012ApJ...753...86T}, and neither star is known to be chemically-peculiar. We suggest that it is possible that these are nevertheless $\alpha^2$\,CVn variables.

>>>>

Two other stars whose variability we classify as rotational modulation, HD~176582 (B5V) and HD~179395 (B9), have very short periods (1.58~d and 1.83~d respectively) and phase stability throughout the \kepler observations. While HD~176582 is listed as an eruptive variable by \citet{2016ApJ...829...23D}, this appears to be a misclassification considering the full \kepler smear light curve. Both stars show periods shorter than the shortest `heartbeat' binaries with tidally-induced pulsations from \citet{2012ApJ...753...86T}. Moreover, the variability periods are short enough that for a binary origin we would expect orbits to be circularized \citep{2000A&A...354..881D}. While neither star is known to be chemically-peculiar, we suggest that it is possible that these are nevertheless $\alpha^2$\,CVn variables.
